\vspace{-20mm}\textbf{ \large \texttt{Placeholder Title:} Retention}

### 2023-07-24 ms.tex
first draft hand out to philipp and jana

\date{\small\today}                                        % kein Datum auf 1. Seite
\title{
	\vspace{-20mm}\textbf{	\large 
	Plankton Retention mechanism studies at Elbe with IBM}
	}
\author{
	Laurin Steidle\(^1\), Ross Vennel, Jana Hinners \\
	\emph{
		\small
		\(^1\)laurin.steidle@uni-hamburg.de} \\
	\emph{
		\small Universitaet Hamburg, Grosse Elbstrasse 133, Germany}
		}

@@

		\begin{abstract}
			\begin{center}
				\texttt{All texts in this typewriter fond are drafting comments and thoughts on the text itself and not part of the actual paper.}
				\smallskip
			\end{center}

			\begin{center}
				\texttt{placeholder abstract - not to be proofread}
				\smallskip
			\end{center}

			% \begin{figure}
			% 	\includegraphics[width=\columnwidth]{picto visual abstract.pdf}
			% \end{figure}
			Estuaries are a challenging environment for plankton.
			Gradients are steep and currents are strong.
			Retention mechanisms are crucial for their survival.
			However, very little experimental and theoretical evidence has been gathered on the mechanism of phytoplankton retention.
			We will conduct a model study.
			First we will show the importance of retention mechanism for plankton in the Elbe.
			Secondly we will study different retention mechanism and comment on their importance.
			\vspace{1cm}
		\end{abstract}
  	\end{@twocolumnfalse}
]

>>>>

\date{\small\today}                                        % kein Datum auf 1. Seite
\title{
	\vspace{-20mm}\textbf{	\large 
	\texttt{Placeholder Title:}  Retention}
	}
\author{
	Laurin Steidle\(^1\), Ross Vennel, Jana Hinners \\
	\emph{
		\small
		\(^1\)laurin.steidle@uni-hamburg.de} \\
	\emph{
		\small Universitaet Hamburg, Grosse Elbstrasse 133, Germany}
		}

@@

		\begin{abstract}
			\begin{center}
				\texttt{All texts in this typewriter font are drafting comments.}
				\smallskip
			\end{center}

			% \begin{figure}
			% 	\includegraphics[width=\columnwidth]{picto visual abstract.pdf}
			% \end{figure}
			\texttt{placeholder abstract: }Estuaries are a challenging environment for plankton.
			Gradients are steep and currents are strong.
			This make retention mechanisms are crucial for their survival.
			However, very little experimental and theoretical evidence has been gathered on the mechanism of phytoplankton retention.
			We will conduct a model study.
			First we will show the importance of retention mechanism for plankton in the Elbe.
			Secondly we will study different retention mechanism and comment on their importance.
			\vspace{1cm}
		\end{abstract}
  	\end{@twocolumnfalse}
]
